Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
Ontributions

\begin{enumerate}
%
\item In this paper we extend the problem of digital control synthesis
  from a transfer function representation into a state space
  representation.  This entails the verification of safety properties
  in addition to the already existing stability conditions which is a
  much harder problem.
%
\item We develop two approaches: the first, naive, one relies on
  explicit unfolding of the system's dynamics up to the completeness
  threshold, whilst the second one is abstraction-based and leverages
  the concepts of abstraction refinement and acceleration to increase speed whilst retaining
  soundness.
%
\item We develop a model for different sources quantization and their
  effect on the state space progression, for which we find safe bounds
  that ensure the safety of our controllers in a hybrid
  continuous-digital domain.
%
\end{enumerate}

>>>>

\begin{enumerate}
%
\item In this paper we extend the problem of digital control synthesis 
from a transfer function representation into a state space representation. 
Such representation allows to study the  input-to-state dynamics, while 
transfer functions represents only input-output relations and cannot be 
enough to ensure deeper properties, e.g. the safety property.
%
\item We proposes a synthesis of state feedback controllers that ensures 
safety properties, that is only  possible in state-space representation. 
In addition to the already existing stability conditions which is a much 
harder problem.
%
\item We develop two approaches: the first, naive, one relies on
  explicit unfolding of the system's dynamics up to the completeness
  threshold, whilst the second one is abstraction-based and leverages
  the concepts of abstraction refinement and acceleration to increase speed whilst retaining
  soundness.
%
\item We develop a model for different sources quantization and their
  effect on the state space progression, for which we find safe bounds
  that ensure the safety of our controllers in a hybrid
  continuous-digital domain.
%
\end{enumerate}
